The role of prenatal conditions on brain mitochondrial physiology and prey detection in a lizard

### 2025-04-07 ms.qmd
updates

Samples examined under the microscope showed a clear presence of neuronal nuclei in the homogenates (Fig. S13). Flow cytometry analysis also confirmed the presence of neuronal nuclei in the homogenates, that were within the size range of the cells employed in the experiment (mean size cells experiment = `r format_dec(mean(mit_df$size), 3)`, 95% CI = [`r format_dec(quantile(mit_df$size, 0.025), 3)`, `r format_dec(quantile(mit_df$size, 0.975), 3)`], n = 80; size neurons = ).

>>>>

```{r, neurons_size}
#| label: neurons_size
# Getting the size of the neurons from the validated data
# Olfactory Bulbs
# A) Experiment cells
cells_exp_OB <- mit_df %>% filter(region == "OB")
mean_cells_size_OB <- format_dec(mean(cells_exp_OB$mean_size), 3)
min_cells_OB <- format_dec(quantile(cells_exp_OB$mean_size, 0.025), 3)
max_cells_OB <- format_dec(quantile(cells_exp_OB$mean_size, 0.975), 3)
# B) Neurons validation
neurons_OB <- read.csv(here("./data/size_neurons_OB.csv")) %>%
  filter(X == "Olfactory Bulb_Tube_001_001.fcs")
neurons_size_OB <- log(neurons_OB$neurons...Geometric.Mean..FSC.A.)
##
##
# Optic Tecta
# A) Experiment cells
cells_exp_OT <- mit_df %>% filter(region == "OT")
mean_cells_size_OT <- format_dec(mean(cells_exp_OT$mean_size), 3)
min_cells_OT <- format_dec(quantile(cells_exp_OT$mean_size, 0.025), 3)
max_cells_OT <- format_dec(quantile(cells_exp_OT$mean_size, 0.975), 3)
# B) Neurons validation
neurons_OT <- read.csv(here("./data/size_neurons_OT.csv")) %>%
  filter(X == "Optical Tecta_Tube_002_002.fcs")
neurons_size_OT <- log(neurons_OT$cells.neurons...Geometric.Mean..FSC.A.)
```

Samples examined under the microscope showed a clear presence of neuronal nuclei in the homogenates (Fig. S13). Flow cytometry analysis also confirmed the presence of neuronal nuclei in the homogenates, that were within the size range of the cells employed in the experiment (mean size cells experiment for OB = `r format_dec(mean(mit_df$mean_size), 3)`, 95% CI = [`r format_dec(quantile(mit_df$mean_size, 0.025), 3)`, `r format_dec(quantile(mit_df$mean_size, 0.975), 3)`], n = 80; size neurons = ).
